Hierarchical Inference of the Intrinsic Ellipticity Distribution of Galaxies during Weak Lensing Analysis

### 2013-04-04 docs/ms.tex
Update ms.tex

\subsection{Measurement Error}

We show some example how our method works when there is an Gaussian
noise added on the observed $\epsilon$

>>>>

\subsection{Measurement Error}
In this section we  discuss how the shape measurement error will
affect the variance and bias of this Hierarchy Bayesian method.As
mentioned before ,we only considers the catalog-level problem of how to combine galaxy ellipticity
measurements.Therefore we assume the likelihood of true lensed ellipticity $p(\epsilon_{ob}|\epsilon_{\ell})
is a 2D Gaussian with sigma equals 0.05 and mean equals true lensed ellipticity.

Therefore the likelihood of $g$ and $\alpha$ becomes
\begin{equation}
L(g,\alpha|\epsilon_{ob})=P(\epsilon_{ob}|g,\alpha)=\intop f(\epsilon_{ob}|\epsilon_{\ell})P(\epsilon_{\ell}|g,\alpha)d\epsilon_{\ell}
\end{equation}
